---
title: "copopa-vignette"
description: >
  This vignette will explain the copopa package.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{copopa-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(copopa)
```

The package does four things:
* It makes checking types of multiple datasets quick.
* It easily saves a dataframe into two different files, CSV and RDS.
* It simultaniously calculates the minimum and maximum.
* It simultaniously calculates the mean and standard deviation.

Checking datatypes is done by the "multi_check(x, y, z)" function. Enter target data as x, y and z and you'll receive a list of types per data set. If you want to check a column of a set enter x$column. If you want to check less than three sets, fill in "NA" for the remaining arguments.

Saving your data frame is done by the "save_to _csv_rds(df, output_name, rownames = ...)". It requires you to enter the target data frame, the names of the output new files and to render rownames or not (TRUE or FALSE).

Calculating the minimum and maximum is done by the "mima(df) function. Just enter target data en you'll receive a list. Data has to be numeric.

Calculating the mean and standard deviation is done by the "mean_sd(df) function. Just enter target data en you'll receive a list. Data has to be numeric.
